---
title: "R Notebook"
output: html_notebook
---
library(RCurl)
existing_cases_file <- getURL("https://docs.google.com/spreadsheets/d/1X5Jp7Q8pTs3KLJ5JBWKhncVACGsg5v4xu6badNs4C7I/pub?gid=0&output=csv")
当X是matrix, c（1，2，3）col

gsub() function replaces all matches of a string
gsub(pattern, replacement, x, ignore.case = FALSE, perl = FALSE,
    fixed = FALSE, useBytes = FALSE)
  可以正则表达
```{r gsub}
x <- "line 4322: He is now 25 years old, and weights 130lbs"
y1 <- gsub("\\d+","---",x)
y1

y2 <- gsub("[[:lower:]]","-",x)
y2

x <- c("R Tutorial","PHP Tutorial", "HTML Tutorial")
gsub("Tutorial","Examples",x)
```
  csv 变量格式 as.string as. integer
```{r dsatasets}
setwd('/Volumes/win/CS/ds/dimred')
existing_df <- read.csv("TB.csv", row.names=1)
existing_df[c(1,2,3,4,5,6,15,16,17,18)] <- 
    lapply( existing_df[c(1,2,3,4,5,6,15,16,17,18)], 
            function(x) { as.integer(gsub(',', '', x) )})
str(existing_df)
```

```{r}
 existing_df[c(1,2)]
```

```{r pca}
pca_existing <- prcomp(existing_df, scale. = TRUE)
str(pca_existing)
summary(pca_existing)
plot(pca_existing)
```
We are interested in the scores, that we have in pca_existing$x
Most variation is explained by the first PC. So let's use the first two PCs to represent all of our countries in a scatterplot.
score-variances
```{r reconstruct}
scores_existing_df <- as.data.frame(pca_existing$x)
# Show first two PCs for head countries
head(scores_existing_df)
```

```{r plot}
biplot(pca_existing)
plot(PC1~PC2, data=scores_existing_df, 
     main= "Existing TB cases per 100K distribution",
     cex = .1, lty = "solid")
text(PC1~PC2, data=scores_existing_df, 
     labels=rownames(existing_df),
     cex=.8)
```
Let's set the color associated with the mean value for all the years. We will use functions rgb, ramp, and rescale to create a color palette from yellow (lower values) to blue (higher values).
```{r coloryear}
library(scales)
ramp <- colorRamp(c("red","yellow", "green","blue"))
colours_by_mean <- rgb( 
    ramp( as.vector(rescale(rowMeans(existing_df),c(0,1)))), 
    max = 255 )
plot(PC1~PC2, data=scores_existing_df, 
     main= "Existing TB cases per 100K distribution",
     cex = .1, lty = "solid", col=colours_by_mean)
text(PC1~PC2, data=scores_existing_df, 
     labels=rownames(existing_df),
     cex=.8, col=colours_by_mean)
```
X2000 similar to PCA1 most

```{r X2000}
library(scales)
ramp <- colorRamp(c("red","yellow", "green","blue"))
colours_by_mean <- rgb( 
    ramp( as.vector(rescale(existing_df$X2000,c(0,1)))), 
    max = 255 )
plot(PC1~PC2, data=scores_existing_df, 
     main= "Existing TB cases per 100K distribution",
     cex = .1, lty = "solid", col=colours_by_mean)
text(PC1~PC2, data=scores_existing_df, 
     labels=rownames(existing_df),
     cex=.8, col=colours_by_mean)
```


```{r changeplot}
existing_df_change <- existing_df$X2008 - existing_df$X1991
ramp <- colorRamp(c("red","yellow", "green","blue"))
colours_by_change <- rgb( 
    ramp( as.vector(rescale(existing_df_change,c(0,1)))), 
    max = 255 )
plot(PC1~PC2, data=scores_existing_df, 
     main= "Existing TB cases per 100K distribution",
     cex = .1, lty = "solid", col=colours_by_change)
text(PC1~PC2, data=scores_existing_df, 
     labels=rownames(existing_df),
     cex=.8, col=colours_by_change)
```
cluster: A vector of integers indicating the cluster to which each point is allocated.
centers: A matrix of cluster centres.
withinss: The within-cluster sum of square distances for each cluster.
size: The number of points in each cluster
```{r kmeans}
set.seed(1234)
existing_clustering <- kmeans(existing_df, centers = 3)
str(existing_clustering)
existing_clustering$centers[1,]
existing_cluster_groups <- existing_clustering$cluster
plot(PC1~PC2, data=scores_existing_df, 
     main= "Existing TB cases per 100K distribution",
     cex = .1, lty = "solid", col=existing_cluster_groups)
text(PC1~PC2, data=scores_existing_df, 
     labels=rownames(existing_df),
     cex=.8, col=existing_cluster_groups)
```
Let's start by creating a line chart that compares the time series for each cluster centroid. This chart will helps us better understand our cluster results
existing_clustering$centers[1,]
```{r cluster}
existing_df$cluster <- existing_clustering$cluster
table(existing_df$cluster)
xrange <- 1990:2007
plot(xrange, existing_clustering$centers[1,], 
     type='l', xlab="Year", 
     ylab="New cases per 100K", 
     col = 1, 
     ylim=c(0,1000))
for (i in 2:nrow(existing_clustering$centers)) {
    lines(xrange, existing_clustering$centers[i,],
    col = i)
}
legend(x=1990, y=1000, 
       lty=1, cex = 0.5,
       ncol = 5,
       col=1:(nrow(existing_clustering$centers)+1),
       legend=paste("Cluster",1:nrow(existing_clustering$centers)))
```

```{r}
for (i in 2:nrow(existing_clustering$centers)){print(rownames(subset(existing_df, cluster==i)))}
```

